%-------------------------
% Resume in LaTeX — Harshibar / jakeryang layout and macros
% TinyTeX-safe preamble (no titlesec/fontawesome5/tgheros if unavailable)
% Section order: Education → Experience → Projects → Leadership \& Campus Roles → Skills \& Other
% Build: pdflatex Resume_EN.tex (twice)
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage[scaled=0.94]{helvet}
\renewcommand*\familydefault{\sfdefault}

\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{0.08}

\hypersetup{pdfauthor={Diyuan Deng}, pdftitle={Resume - Diyuan Deng}}

\pagestyle{empty}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{0in}

% Slightly roomier body lines (readable on 11pt sans)
\linespread{1.045}\selectfont

% Mimics \titleformat{\section}{...}[\color{light-grey}\titlerule[2pt]\vspace{-4pt}]
\newcommand{\resumeSection}[1]{%
  \par\vspace{0.42em plus 0.06em minus 0.03em}%
  {\large\bfseries\raggedright #1\par}%
  \nointerlineskip
  {\color{light-grey}\rule{\linewidth}{2pt}}%
  \par\vspace{0.14em plus 0.04em minus 0.02em}%
}

\newcommand{\resumeItem}[1]{%
  \item\small{#1}%
}

\newcommand{\resumeSubheading}[4]{%
  \item
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & {\color{dark-grey}\small#2}\\[0.08em]
    \textit{#3} & {\color{dark-grey}\small#4}\\
  \end{tabular*}\vspace{-2pt}%
}

\newcommand{\resumeProjectHeading}[2]{%
  \item
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    #1 & {\color{dark-grey}\small#2}\\
  \end{tabular*}\vspace{-2pt}%
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newenvironment{resumeSubHeadingList}{%
  \begin{list}{}{%
      \setlength{\leftmargin}{0pt}%
      \setlength{\itemindent}{0pt}%
      \setlength{\labelwidth}{0pt}%
      \setlength{\labelsep}{0pt}%
      \setlength{\itemsep}{0.22em plus 0.04em minus 0.03em}%
      \setlength{\parsep}{0pt}%
      \setlength{\topsep}{0pt}%
      \setlength{\partopsep}{0pt}%
    }%
}{\end{list}}
\newcommand{\resumeSubHeadingListStart}{\begin{resumeSubHeadingList}}
\newcommand{\resumeSubHeadingListEnd}{\end{resumeSubHeadingList}}
\newcommand{\resumeItemListStart}{%
  \begingroup
  \setlength{\itemsep}{0.16em plus 0.03em minus 0.02em}%
  \setlength{\parsep}{0pt}%
  \setlength{\topsep}{0.12em}%
  \setlength{\partopsep}{0pt}%
  \begin{itemize}%
}
\newcommand{\resumeItemListEnd}{\end{itemize}\endgroup}

\color{text-grey}

%-------------------------------------------
\begin{document}

\newcommand{\FullName}{Diyuan Deng}
\newcommand{\Email}{diyuandeng@link.cuhk.edu.cn}
\newcommand{\Phone}{+86~153~0153~9901}
\newcommand{\Location}{Shenzhen, China}
\newcommand{\Github}{https://github.com/aCm1T}

%----------HEADING (template-style contact line)----------
\begin{center}
  \textbf{\Huge\FullName} \\ \vspace{5pt}
  \small
  \texttt{\Phone} \hspace{1pt} $|$
  \hspace{1pt} \href{mailto:\Email}{\texttt{\Email}} \hspace{1pt} $|$
  \hspace{1pt} \href{\Github}{\texttt{github.com/aCm1T}} \hspace{1pt} $|$
  \hspace{1pt} \texttt{\Location}
  \\ \vspace{-3pt}
\end{center}

%-----------EDUCATION-----------
\resumeSection{EDUCATION}
\resumeSubHeadingListStart

  \resumeSubheading
    {The Chinese University of Hong Kong, Shenzhen}{Sep 2023 -- Jun 2027 (Expected)}
    {B.Sc., Data Science and Big Data Technology}{Shenzhen, China}
    \resumeItemListStart
      \resumeItem{GPA: \textbf{3.43} / 4.0; coursework: databases, algorithms, stochastic processes, optimization, machine learning, statistical computing.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\resumeSection{EXPERIENCE}
\resumeSubHeadingListStart

  \resumeSubheading
    {Shanghai Wuzhi Evolution Technology Co., Ltd.\ (Embodied Data R\&D)}{Jun 2025 -- Aug 2025}
    {Data Engineering Intern}{Shanghai, China}
    \resumeItemListStart
      \resumeItem{Collaborated with Prof.\ Bo Zhao's research group (Shanghai Jiao Tong University) on embodied AI data and VLA model development.}
      \resumeItem{Built an \textbf{xArm} \textbf{data acquisition pipeline} and contributed to \textbf{VLA} optimization (\textbf{10,000+} trajectories); adapted to \textbf{LeRobot}, integrated multimodal LLMs with \textbf{NL commands}, and reached \textbf{$>$90\%} success on grasping/stacking.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\resumeSection{PROJECTS}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Enterprise LLM Inference (SFGlang)} $|$ Core Developer, SF Technology Co., Ltd.}{Jan 2026 -- Present}
    \resumeItemListStart
      \resumeItem{Improved throughput and communication for \textbf{Qwen3}-class LLMs and multimodal models (\textbf{4B / 30B}) under enterprise concurrency.}
      \resumeItem{Deployed \textbf{SGLang} with \textbf{dual-container isolation}; tuned \textbf{4090} clusters (\textbf{PD/EPD}, \textbf{TP/DP/EP}, \textbf{FP8/INT8}); \textbf{load-testing web platform}; \textbf{two} patents (in progress). \textbf{Qwen-30B} \textbf{TP4+DP2}: \textbf{$-$48.9\% TTFT}, \textbf{+664\%} throughput; \textbf{Qwen-4B} \textbf{TP1+DP2}: \textbf{+750\%} (quantize first, minimize TP, maximize DP).}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{NSC-Advisor: Ischemic Stroke Prognosis} $|$ Research Assistant}{Sep 2025 -- Dec 2025}
    \resumeItemListStart
      \resumeItem{{\footnotesize Manuscript submitted to \textbf{ISMRM} (under review).}}
      \resumeItem{Built an interpretable \textbf{favorable vs.\ unfavorable} prognosis pipeline (few-shot, prompting, \textbf{RAG}); dual-input UI with visualizations; \textbf{93.75\%} on \textbf{16} held-out cases.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Library Management System} $|$ Developer}{Sep 2024 -- Nov 2024}
    \resumeItemListStart
      \resumeItem{Developed a full-stack \textbf{Python (tkinter) + SQLite} application with four normalized tables, composite indexes, and \textbf{15+} features including \textbf{SHA-256} authentication and an admin dashboard; tests covered \textbf{100\%} of requirements.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{2D RPG Combat (Unreal Engine 5 \& C++)} $|$ Developer}{Sep 2024 -- Dec 2024}
    \resumeItemListStart
      \resumeItem{Implemented \textbf{C++} combat logic and three enemy AI archetypes; built a \textbf{Qt} launcher with \textbf{SHA-256} messaging; used \textbf{PaperZD} for animation state machines; contributed \textbf{1,000+} lines of core team code; project recognized as \textbf{best course project}.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------LEADERSHIP \& CAMPUS ROLES-----------
\resumeSection{LEADERSHIP \& CAMPUS ROLES}
\begin{resumeSubHeadingList}
  \small
  \item{%
    \textbf{Undergraduate Student Teaching Fellow:} Instructed \textbf{10+} tutorials (\textbf{800+} students) for \textbf{Data Structures} \& \textbf{Databases}; awarded \textbf{SDS Excellent USTF} (2024--2025).\\[0.32em]
    \textbf{Student Assistant,} University Library (Nov 2023--Present): industrial 3D printers (\textbf{X1E}, \textbf{Ultimaker S5}, \textbf{Form~2}), \textbf{30+} jobs; \textbf{10+} edits (FCP, Photoshop); 3D-printing workshops.\\[0.32em]
    \textbf{Founder \& Vice President,} 2Tired Cycling Club (Jul 2024--Present): core team \textbf{20}, five functions; community rides \& Tour de France meet-ups; Y1 \textbf{80+} members, \textbf{95\%} satisfaction.%
  }
\end{resumeSubHeadingList}

%-----------SKILLS \& OTHER-----------
\resumeSection{SKILLS \& OTHER}
\begin{resumeSubHeadingList}
  \small
  \item{%
    \textbf{Awards}{: Third Prize, Guangdong Division, China Undergraduate Mathematical Contest in Modeling (2025)}\\[0.28em]
    \textbf{Languages}{: Chinese (native); English (professional proficiency for coursework and internships.)}\\[0.28em]
    \textbf{Programming / ML / tools}{: \textbf{Python} (advanced), \textbf{SQL}, C++, R; \textbf{UE5}, tkinter, Qt; LLM serving (\textbf{SGLang}, parallelism, quantization); Git; Linux-style workflows.}\\[0.28em]
    \textbf{Interests}{: Cycling, photography, hiking, amateur radio, Model United Nations.}
  }
\end{resumeSubHeadingList}

\end{document}
